
\begin{thebibliography}{99}
\phantomsection \label{References}
\addcontentsline{toc}{section}{References}
{\fontfamily{lmtt}\selectfont\scriptsize


\setlength{\itemsep}{3pt}

\bibitem{MirandaAnderson}
Miranda Anderson, \i{et. al.},
\cq{Distributed Cognition and the
Humanities}.
\biburl{https://marksprevak.com/pdf/paper/AndersonWheelerSprevak---Distributed\%20cognition\%20and\%20the\%20humanities.pdf}.


\bibitem{EricArnau}
Eric Arnau, \i{et. al.},
\cq{The Extended Cognition Thesis: Its significance for the philosophy of (cognitive) science}.
\biburl{https://www.tandfonline.com/doi/full/10.1080/09515089.2013.836081}.



\bibitem{GregoryBerns}
Gregory Berns, 
\bibtitle{How Dogs Love Us}.
Houghton Mifflin, 2013.



\bibitem{BernsWhatItsLike}
Gregory Berns, 
\bibtitle{What It's Like to be a Dog: 
And other adventures in animal neuroscience}.
Basic Books, 2017.



\bibitem{CharlesSBrown}
Charles S. Brown
\cq{The Intentionality and Animal Heritage of Moral Experience:
What We can Learn from Dogs About Moral Theory}.
\biburl{https://link.springer.com/chapter/10.1007/978-1-4020-6307-7_7}



\bibitem{CameronBuckner}
Cameron Buckner,
\cq{The Semantic Problem(s) with Research on Animal Mind-Reading}.
\biburl{http://cameronbuckner.net/professional/semanticproblems.pdf}



\bibitem{SusanCarey}
Susan Carey,
\cq{Do Constraints on Word Meanings Reflect Prelinguistic 
Cognitive Architecture}.
\biburl{https://www.harvardlds.org/wp-content/uploads/2018/05/Carey.-1997.-Do-constraints-on-word-meanings-reflect-prelinguistic-cognitive-architecture.pdf}



\bibitem{DavidChalmers}
David Chalmers,
\cq{Extended Cognition and Extended Consciousness}.
\biburl{https://philarchive.org/archive/CHAECA-9}



\bibitem{StanleyCoren}
Stanley Coren,
\bibtitle{The Intelligence of Dogs}.
Free Press, 1994.


\bibitem{EdoardoDatteri}
Edoardo Datteri, \i{et. al.},
\cq{Going Beyond the \q{Synthetic Method}: New Paradigms Cross-Fertilizing Robotics and Cognitive Neuroscience}.
\biburl{https://www.frontiersin.org/articles/10.3389/fpsyg.2022.819042/full}.


\bibitem{BenoitDenizetLewis}
Benoit Denizet-Lewis, 
\bibtitle{Travels with Casey}.
Simon \& Schuster, 2014.



\bibitem{AnnaFrohnwiese}
Anna Frohnwiese, \i{et. al.},
\cq{Using Robots to Understand Animal Cognition}.
\biburl{https://pubmed.ncbi.nlm.nih.gov/26781049/}.



\bibitem{RiccardoFusaroli}
Riccardo Fusaroli, \i{et. al.},
\cq{The Dialogically Extended Mind: Language as skilful
intersubjective engagement}.
\biburl{https://pure.au.dk/ws/files/55171506/2013_cognitive_systems_research_Dialogically_Extended_Mind.pdf}.


\bibitem{HajoGreif}
Hajo Greif,
\cq{What is the Extension of the Extended Mind?}.
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5686289/}.



\bibitem{HareWoods}
Brian Hare and Vanessa Woods, 
\bibtitle{Survival of the Friendliest: Understanding Our Origins and Rediscovering Our Common Humanity}.
Random House, 2020.


\bibitem{HareGeniusofDogs}
Brian Hare and Vanessa Woods, 
\bibtitle{The Genius of Dogs}.
Penguin, 2013.



\bibitem{HoffmannPfeife}
Matej Hoffmann and Rolf Pfeife, \i{et. al.},
\cq{Robots as Powerful Allies for the Study
of Embodied Cognition from the
Bottom Up}.
\biburl{https://philarchive.org/archive/HOFRAP-2}.





\bibitem{ChristinaHunger}
Christina Hunger, 
\bibtitle{How Stella Learned to Talk: The 
Groundbreaking Story of the World's First Talking Dog}.
Harper Collins, 2021.



\bibitem{SimonPJames}
Simon P. James, 
\cq{Phenomenology and the Problem of Animal Minds}.
\biburl{https://www.environmentandsociety.org/mml/phenomenology-and-problem-animal-minds}



\bibitem{KaminskiPiotti}
Juliane Kaminski and Patrizia Piotti, 
\cq{Current Trends in Dog-Human Communication: Do dogs inform?}.
\biburl{https://journals.sagepub.com/doi/abs/10.1177/0963721416661318}


\bibitem{JulianeKaminski}
Juliane Kaminski, \i{et. al.}, 
\cq{Domestic Dogs Comprehend Human Communication with
Iconic Signs}.
\biburl{https://asset-pdf.scinapse.io/prod/2148275342/2148275342.pdf}


\bibitem{KaminskiRico}
Juliane Kaminski, \i{et. al.}, 
\cq{Word Learning in a Domestic Dog: Evidence for
\q{Fast Mapping}}.
\biburl{https://quote.ucsd.edu/cogs156/files/2013/03/Kaminski05Rico.pdf}




\bibitem{RonaldLangacker}
Ronald Langacker, 
\cq{Interactive Cognition: Toward a Unified Account of Structure, Processing, and Discourse}.
\biburl{https://search.proquest.com/openview/8f77fd4dc8af81470c9cc73483c0c6e7/1?pq-origsite=gscholar&cbl=2034870}



\bibitem{DominiqueLestel}
Dominique Lestel, \i{et. al.}, 
\cq{The Phenomenology of Animal Life}.
\biburl{https://pdfs.semanticscholar.org/6a7d/9b86779a783ed92ebf42f70170911667f5a7.pdf}








\bibitem{DieterLohmar}
Dieter Lohmar,
\cq{How do Primates Think? Phenomenological Analyses of Non-language Systems of Representation in Higher Primates and Humans}.
\biburl{https://link.springer.com/chapter/10.1007/978-1-4020-6307-7_5}



\bibitem{DieterLohmarIntercultural}
\_\_\_\_\_,
\cq{Language as Means and as an Obstacle  of Communication: Phenomenological grounds for intercultural understanding}.
\biburl{https://revistes.uab.cat/enrahonar/article/view/v57-lohmar/1023-pdf-en}



\bibitem{MelliesZeilberger}
Paul-Andr\'e Melli\`es and Noam Zeilberger,
\cq{Parsing as a Lifting Problem and the
Chomsky-Sch\"utzenberger Representation Theorem}.
\biburl{https://hal.archives-ouvertes.fr/hal-03702762/document} 




\bibitem{NeemehFavela}
Zachariah A. Neemeh and Luis H. Favela,
\cq{Beyond Distributed Cognition: Towards a Taxonomy of Nonreductive Social
Cognition}.
\biburl{https://cogsci.mindmodeling.org/2017/papers/0528/paper0528.pdf} 



\bibitem{PainterLotz}
Corinne Painter and Christian Lotz,
\bibtitle{Phenomenology and the Non-Human Animal: At the Limits of Experience}.
Springer, 2007.


\bibitem{PilleyHinzmann}
John W Pilley and Hilary Hinzmann, 
\bibtitle{Chaser: Unlocking the genius of the dog who knows 1000 words}.
Houghton Mifflin, 2013.


\bibitem{StevenPinker}
Steven Pinker,  
\bibtitle{The Language Instinct}.
William Morrow, 1994. 



\bibitem{KatieARiddoch}
Katie A. Riddoch, \i{et. al.}, 
\cq{Exploring Behaviours Perceived as Important
for Human—Dog Bonding and their
Translation to a Robotic Platform}.
\biburl{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0274353}



\bibitem{MarkRowlands}
Mark Rowlands, \i{et. al.}, 
\cq{Extended Cognition and the Mark of the Cognitive}.
\biburl{https://www.ida.liu.se/~729A10/mtrl/Rowlands.pdf}



\bibitem{KennethJShapiro}
Kenneth J. Shapiro, 
\cq{What it is to be a Dog: A Qualitative Method for the Study of
Animals Other than Humans}.
\biburl{https://www.wellbeingintlstudiesrepository.org/cgi/viewcontent.cgi?article=1081&context=acwp_arte}



\bibitem{ConSlobodchikoff}
Con Slobodchikoff,  
\bibtitle{Chasing Doctor Dolittle: Learning the Language of Animals}.
St. Martin's, 2012. 



\bibitem{PaulRSmart}
Paul R. Smart, 
\cq{Toward a Mechanistic Account of Extended
Cognition}.
\biburl{https://eprints.soton.ac.uk/454082/2/Toward_a_Mechanistic_Account_of_Extended_Cognition.pdf}




\bibitem{MichaelTomasello}
Michael Tomasello, 
\bibtitle{The Cultural Origins of Human Cognition}.
Harvard University Press, 1999.
\biburl{http://ektr.uni-eger.hu/wp-content/uploads/2015/11/tomasello-the-cultural-origins-of-human-cognition.pdf}



\bibitem{JamesLYu}
James L. Yu, 
\cq{A Phenomenological-Hermeneutic Analysis of
Experimental Infant Research}.
Dissertation, Duquesne University, 2009.
\biburl{https://dsc.duq.edu/cgi/viewcontent.cgi?article=2410&context=etd}



\bibitem{VanessaWoods}
Vanessa Woods, 
\bibtitle{Bonobo Handshake}.
Gothan Books, 2010.


\bibitem{ZhangPatel}
Jiajie Zhang and Vimla L. Patel, 
\cq{Distributed Cognition, Representation, and Affordance}.
\biburl{https://psycnet.apa.org/record/2006-21234-010}



\bibitem{ZentallPattison}
Thomas R. Zentall and Kristina F. Pattison, 
\cq{Now You See It, Now You Don't: Object Permanence in Dogs}.
\biburl{https://www.jstor.org/stable/44318955}


}
\end{thebibliography}


