
\begin{thebibliography}{99}
\phantomsection \label{References}
\addcontentsline{toc}{section}{References}
{\fontfamily{lmtt}\selectfont\scriptsize


\bibitem{RadhakrishnaAchanta}
Radhakrishna Achanta, \i{et. al.},
\cq{SLIC Superpixels Compared
to State-of-the-Art Superpixel Methods}.
\biburl{https://www.cs.jhu.edu/~ayuille/JHUcourses/VisionAsBayesianInference2022/4/Achanta_SLIC_PAMI2012.pdf} 



\bibitem{MartinCadik}
Martin \v{C}ad\'{\OldI}k,
\cq{Perceptual Evaluation of Color-to-Grayscale Image Conversions}.
\biburl{http://cadik.posvete.cz/color_to_gray_evaluation/cadik08perceptualEvaluation.pdf} 


\bibitem{ChadwickKentridge}
A.C. Chadwick and R.W. Kentridge,
\cq{The perception of gloss: A review}.
\biburl{https://pubmed.ncbi.nlm.nih.gov/25448119} 


\bibitem{ChanRiek}
Darren M. Chan and Laurel D. Riek,
\cq{Object Proposal Algorithms in the Wild: 
Are they Generalizable to Robot Perception?}.
\biburl{https://cseweb.ucsd.edu/~lriek/papers/chan-riek-IROS2019.pdf} 


\bibitem{ChenWang}
Jim X. Chen and Xusheng Wang,
\cq{Approximate Line Scan-Conversion and its Hardware Design}.
\biburl{https://cs.gmu.edu/~jchen/report/hardwareLine.pdf} 


\bibitem{MingliangChen}
Mingliang Chen, \i{et. al.},
\cq{Interactive Hierarchical Object Proposals}.
\biburl{http://www.shengfenghe.com/qfy-content/uploads/2019/12/458b6d07423a8844d3129412b717a0b3.pdf} 


\bibitem{MingMingCheng}
Ming-Ming Cheng, \i{et. al.},
\cq{Deep Hough Transform for Semantic Line Detection}.
\biburl{https://arxiv.org/pdf/2003.04676.pdf} 


\bibitem{GideonKanjiDamaryam}
Gideon Kanji Damaryam,
\cq{A Method to Determine End-Points ofStraight Lines Detected Using the Hough
Transform}.
\biburl{https://www.ijera.com/papers/Vol6_issue1/Part\%20-\%201/H601016775.pdf} 


\bibitem{DavitGigilashvili}
Davit Gigilashvili, \i{et. al.},
\cq{Perceived Glossiness: Beyond Surface Properties}.
\biburl{https://jbthomas.org/Conferences/2019aCIC.pdf} 


\bibitem{XiaoyingGuo}
Xiaoying Guo, \i{et. al.},
\cq{Analysis of Texture Characteristics Associated with Visual Complexity Perception}.
\biburl{https://link.springer.com/article/10.1007/s10043-012-0047-1} 



\bibitem{BumsubHam}
Bumsub Ham, \i{et. al.},
\cq{Proposal Flow: Semantic Correspondences from
Object Proposals}.
\biburl{https://www.di.ens.fr/willow/pdfscurrent/ham2017.pdf} 



\bibitem{KunimatsuHashimoto}
Kunimatsu Hashimoto, \i{et. al.},
\cq{KOSNet: A Unified Keypoint, Orientation and Scale Network for
Probabilistic 6D Pose Estimation}.
\biburl{http://groups.csail.mit.edu/robotics-center/public_papers/Hashimoto20.pdf} 



\bibitem{ZheyuanHu}
Zheyuan Hu, \i{et. al.},
\cq{Object Pose Estimation for Robotic Grasping based
on Multi-view Keypoint Detection}.
\biburl{http://www.cloud-conf.net/ispa2021/proc/pdfs/ISPA-BDCloud-SocialCom-SustainCom2021-3mkuIWCJVSdKJpBYM7KEKW/264600b295/264600b295.pdf} 


\bibitem{CsabaIstvanKiss}
Csaba Istv\'an Kiss, \i{et. al.},
\cq{On Feature Extraction for Texture Analysis}.
\biburl{https://core.ac.uk/download/pdf/236628682.pdf} 



\bibitem{SifanJi}
Sifan Ji, \i{et. al.},
\cq{Image Clustering Algorithm using Superpixel
Segmentation and Non-Symmetric Gaussian–
Cauchy Mixture Model}.
\biburl{https://ietresearch.onlinelibrary.wiley.com/doi/pdf/10.1049/iet-ipr.2020.0402} 


\bibitem{ZequnJie}
Zequn Jie, \i{et. al.},
\cq{Scale-Aware Pixelwise Object Proposal Networks}.
\biburl{https://www.sysu-hcp.net/userfiles/files/2021/02/28/3a62f36bc1fe7fb9.pdf} 


\bibitem{VRJyothish}
V. R. Jyothish, \i{et. al.},
\cq{An Efficient Image Segmentation Approach using Superpixels with Colorization}.
\biburl{https://www.sciencedirect.com/science/article/pii/S1877050920310620} 



\bibitem{KrahenbuhlKoltun}
Philipp Kr\"ahenb\"uhl and Vladlen Koltun,
\cq{Geodesic Object Proposals}.
\biburl{http://vladlen.info/papers/gop.pdf} 



\bibitem{GiovaneRKuhn}
Giovane R. Kuhn, \i{et. al.},
\cq{An Improved Contrast Enhancing Approach for Color-to-Grayscale Mappings}.
\biburl{https://www.inf.ufrgs.br/~oliveira/pubs_files/MS_C2G/Kuhn_Oliveira_Color_to_Gray_TVCJ_Pre-print.pdf} 


\bibitem{RushiLan}
Rushi Lan, \i{et. al.},
\cq{Quaternionic Local Ranking Binary Pattern:
A Local Descriptor of Color Images}.
\biburl{https://ieeexplore.ieee.org/document/7350143} 



\bibitem{StefanLeutenegger}
Stefan Leutenegger, \i{et. al.},
\cq{BRISK: Binary Robust Invariant Scalable Keypoints}.
\biburl{https://margaritachli.com/papers/ICCV2011paper.pdf} 



\bibitem{NannanLiao}
Nannan Liao, \i{et. al.},
\cq{BACA: Superpixel Segmentation with Boundary Awareness
and Content Adaptation}.
\biburl{https://www.mdpi.com/2072-4292/14/18/4572} 



\bibitem{LimIsa}
Wei Hong Lim and Nor Ashidi Mat Isa,
\cq{Color to Grayscale Conversion Based On 
Neighborhood Pixels Effect Approach for Digital Image}.
\biburl{https://www.emo.org.tr/ekler/14281fad9e3d0cc_ek.pdf} 


\bibitem{MaikoMILie}
Maiko M. I. Lie, \i{et. al.},
\cq{Joint Upsampling of Random Color Distance Maps for Fast Salient Region Detection}.
\biburl{https://www.sciencedirect.com/science/article/abs/pii/S0167865517303215} 



\bibitem{LiuAldrich}
Xiu Liu and Chris Aldrich,
\cq{Deep Learning Approaches to Image Texture Analysis in
Material Processing}.
\biburl{https://mdpi-res.com/d_attachment/metals/metals-12-00355/article_deploy/metals-12-00355-v3.pdf?version=1645497882} 



\bibitem{LuShapiro}
Yao Lu and Linda Shapiro,
\cq{Closing the Loop for Edge Detection and Object Proposals}.
\biburl{https://homes.cs.washington.edu/~shapiro/yao-aaai.pdf} 


\bibitem{MajiMalik}
Subhransu Maji and Jitendra Malik,
\cq{Object Detection using a Max-Margin Hough Transform}.
\biburl{https://www2.eecs.berkeley.edu/Research/Projects/CS/vision/shape/smaji-cvpr09.pdf} 



\bibitem{MirjaliliHardeberg}
Fereshteh Mirjalili and Jon Yngve Hardeberg,
\cq{On the Quantification of Visual Texture Complexity}.
\biburl{https://www.mdpi.com/2313-433X/8/9/248} 



\bibitem{LaszloNeumann}
L\'aszl\'o Neumann, \i{et. al.},
\cq{An Efficient Perception-based Adaptive Color to Gray Transformation}.
\biburl{https://diglib.eg.org/bitstream/handle/10.2312/COMPAESTH.COMPAESTH07.073-080/073-080.pdf?sequence=1} 


\bibitem{NguyenHavlicek}
Chuong T. Nguyen and Joseph P. Havlicek
\cq{Color to Grayscale Image Conversion using Modulation Domain Quadratic Programming}.
\biburl{https://ieeexplore.ieee.org/document/7351674} 


\bibitem{ShinyaNishida}
Shin'ya Nishida
\cq{Image Statistics for Material Perception}.
\biburl{https://www.sciencedirect.com/science/article/pii/S235215461930035X} 



\bibitem{PapushaHo}
Ivan Papusha and Matthew Ho,
\cq{Hough Transform for Directional Orientation}.
\biburl{https://stacks.stanford.edu/file/druid:rz261ds9725/Ho_Papusha_RealTimeHoughTransform.pdf} 


\bibitem{GiorgosSfikas}
Giorgos Sfikas, \i{et. al.},
\cq{Quaternion Harris For Multispectral Keypoint Detection}.
\biburl{https://www.cs.uoi.gr/~sfikas/icip-quatharris.pdf} 


\bibitem{JordiPontTuset}
Jordi Pont-Tuset, \i{et. al.},
\cq{Multiscale Combinatorial Grouping for Image Segmentation and
Object Proposal Generation}.
\biburl{https://upcommons.upc.edu/bitstream/handle/2117/105287/1503.00848.pdf} 


\bibitem{AntonioRubio}
Antonio Rubio, \i{et. al.},
\cq{BASS: Boundary-Aware Superpixel Segmentation}.
\biburl{https://digital.csic.es/bitstream/10261/166227/1/bassbound.pdf} 





\bibitem{HadiSutopo}
Hadi Sutopo,
\cq{Bresenham's Lines Algorithm Visualization Using Flash}.
\biburl{https://ggn.dronacharya.info/ITDept/Downloads/QuestionBank/Odd/V\%20sem/Bresenham_Lines_Algorithm_Visualization_Flash_IIISem.pdf} 


\bibitem{MihranTuceryan}
Mihran Tuceryan and Anil K. Jain,
\cq{Texture Analysis}.
\biburl{https://cs.iupui.edu/~tuceryan/research/ComputerVision/texture-review.pdf} 


\bibitem{TakeshiUejima}
Takeshi Uejima, \i{et. al.},
\cq{Proto-Object Based Saliency Model With Texture Detection Channel}.
\biburl{https://www.frontiersin.org/articles/10.3389/fncom.2020.541581/pdf} 



\bibitem{MinglongXue}
Minglong Xue, 
\cq{Deep invariant texture features for water image classifcation}.
\biburl{https://link.springer.com/content/pdf/10.1007/s42452-020-03882-w.pdf} 


\bibitem{XinmingWang}
Xinming Wang, 
\cq{Real-time Classified Hough Transform Line Detection Based on FPGA}.
\biburl{https://www.atlantis-press.com/article/25848213.pdf} 


\bibitem{WangYong}
Zhi-Zhong Wang and Jun-Hai Yong,
\cq{Texture Analysis and Classification With Linear
Regression Model Based on Wavelet Transform}.
\biburl{https://hal.inria.fr/inria-00517305/document} 


\bibitem{WendtFaul}
Gunnar Wendt and Franz Faul,
\cq{Factors Influencing the
Detection of Spatially-Varying
Surface Gloss}.
\biburl{https://journals.sagepub.com/doi/pdf/10.1177/2041669519866843} 



\bibitem{JianpingWu}
Jianping Wu, \i{et. al.},
\cq{Real-time Vanishing Point Detector Integrating Under-parameterized RANSAC
and Hough Transform}.
\biburl{https://openaccess.thecvf.com/content/ICCV2021/papers/Wu_Real-Time_Vanishing_Point_Detector_Integrating_Under-Parameterized_RANSAC_and_Hough_Transform_ICCV_2021_paper.pdf} 




\bibitem{YiXuanZhan}
Yi-Xuan Zhan, \i{et. al.},
\cq{Superpixel Segmentation Using Improved Lazy Random
Walk Framework Based on Texture Complexities}.
\biburl{http://www.csroc.org.tw/journal/JOC30_5/JOC-3005-20.pdf} 



\bibitem{ZhangTorr}
Ziming Zhang and Philip H.S. Torr,
\cq{Object Proposal Generation using Two-Stage
Cascade SVMs}.
\biburl{https://zimingzhang.files.wordpress.com/2014/10/ziming_tpami_obj_proposal_final.pdf} 


\bibitem{HanliZhao}
Hanli Zhao, \i{et. al.},
\cq{Image Recoloring using Geodesic Distance Based Color
Harmonization}.
\biburl{https://core.ac.uk/download/pdf/81904494.pdf} 



\bibitem{YuZhou}
Yu Zhou, \i{et. al.},
\cq{Object-level Proposals}.
\biburl{https://openaccess.thecvf.com/content_ICCV_2017/papers/Ma_Object-Level_Proposals_ICCV_2017_paper.pdf} 


\bibitem{ZitnickDollar}
C. Lawrence Zitnick and Piotr Doll\'ar
\cq{Edge Boxes: Locating
Object Proposals from Edges}.
\biburl{https://link.springer.com/content/pdf/10.1007/978-3-319-10602-1_26.pdf} 


\bibitem{JanaZujovic}
Jana Zujovic,
\cq{Structural Texture Similarity Metrics for Image
Analysis and Retrieval}.
\biburl{http://users.eecs.northwestern.edu/~pappas/papers/zujovic_tip13.pdf} 




}
\end{thebibliography}


