
\begin{thebibliography}{99}
\phantomsection \label{References}
\addcontentsline{toc}{section}{References}
{\fontfamily{lmtt}\selectfont\scriptsize

\bibitem{RaubalAdams}
Benjamin Adams and Martin Raubal, 
\cq{A Metric Conceptual Space Algebra}.
\biburl{https://pdfs.semanticscholar.org/521a/cbab9658df27acd9f40bba2b9445f75d681c.pdf}

\bibitem{RaubalAdamsCSML}
Benjamin Adams and Martin Raubal, 
\cq{Conceptual Space Markup Language (CSML): Towards the Cognitive Semantic Web}.
\biburl{http://idwebhost-202-147.ethz.ch/Publications/RefConferences/ICSC_2009_AdamsRaubal_Camera-FINAL.pdf}

\bibitem{AsherPustejovsky}
Nicholas Asher and James Pustejovsky, 
\cq{A Type Composition Logic for Generative Lexicon}
\biburl{https://www.cs.brandeis.edu/~jamesp/classes/cs216-2009/readings2009/TCLforGL.pdf}


\bibitem{BarkerShanTG}
Chris Barker and Chung-Chieh Shan, 
\cq{Types as Graphs: Continuations in Type Logical Grammar}
\biburl{https://www.nyu.edu/projects/barker/barker-shan-types-as-graphs.pdf}

%
\bibitem{Belohlavek}
Radim B\v{e}lohl\'avek and Vladim{\i\OldI}r Sklen\'a\v{r}, 
\cq{Formal Concept Analysis Constrained by Attribute-Dependency Formulas}
B. Ganter and R. Godin, eds.,: ICFCA 2005, LNCS 3403, pp. 176-191, Berlin, Springer-Verlag, 2005.
\biburl{http://belohlavek.inf.upol.cz/publications/BeSk_Fcacadf.pdf}

\bibitem{JiriBenovsky}
Juri Benovsky, 
\cq{Two Concepts of Possible Worlds – or Only One?}.  
THEORIA, 2008, volume 74, pp. 318–330.
\biburl{http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.464.3904&rep=rep1&type=pdf}



\bibitem{BernardyEtAl}
Jean-Philippe Bernardy, \i{et. al.},
\cq{Parametricity and Dependent Types}.
\biburl{http://www.staff.city.ac.uk/~ross/papers/pts.pdf}

\bibitem{BiskriDescles}
Isma{\"\OldI}l Biskri and Jean-Pierre Descles, 
\cq{Applicative and Combinatory Categorial Grammar 
(from syntax to functional semantics)}
\biburl{https://www.researchgate.net/publication/232754402_Applicative_and_Combinatory_Categorial_Grammar_from_syntax_to_functional_semantics}

\bibitem{BittnerSmithDonnelly}
Thomas Bittner, Barry Smith, and Maureen Donnelly,
\cq{The logic of systems of granular partitions.}
\biburl{http://ontology.buffalo.edu/smith/articles/BittnerSmithDonnelly.pdf}


\bibitem{MathieuBouchard}
Mathieu Bouchard, 
\cq{A Type Theory for the Documentation of PureData}
\biburl{http://artengine.ca/~catalogue-pd/43-Bouchard.pdf}

\bibitem{LineBrandt}
Line Brandt, 
\cq{The Communicative Mind.}
Newcastle-upon-Tyne: Cambridge Scholars Publishing, 2013

%
\bibitem{PerAageBrandt}
Per Aage Brandt, 
\cq{Spaces, Domains, and Meaning: Essays in Cognitive Semiotics}.
Newcastle-upon-Tyne: Cambridge Scholars Publishing, 2013
\biburl{http://semiotics.au.dk/fileadmin/Semiotics/pdf/per-aage-brandt/Per_Aage_Brandt__Spaces__Domains__and_Meaning._Essays_in_Co.pdf}



\bibitem{ChatzikyriakidisLuo}
Stergios Chatzikyriakidis and Zhaohui Luo, 
\cq{Individuation Criteria, Dot-types and Copredication: A View from Modern Type Theories.}
\intitle{Association for Computational Linguistics, Proceedings of the 14th 
Meeting on the Mathematics of Language (MoL 14)}, pp. 39–50, 2015. 
\biburl{http://www.aclweb.org/anthology/W15-2304}

\bibitem{ChoeCharniak}
Do Kook Choe and Eugene Charniak, 
\cq{Parsing as Language Modeling}.
\tinyurl{https://aclweb.org/anthology/D16-1257}


\bibitem{InteractingConceptualSpaces}
Bob Coecke, \i{et. al.}, 
\cq{Interacting Conceptual Spaces I:
Grammatical Composition of Concepts}.
\biburl{https://arxiv.org/pdf/1703.08314.pdf}

\bibitem{Descles2010}
Jean-Pierre Descl\'es, \cq{Reasoning in Natural Language in 
	Using Combinatory Logic and Topology: An Example with Aspect
	and Temporal Relations.}  
\biburl{https://www.aaai.org/ocs/index.php/FLAIRS/2010/paper/viewFile/1350/1736}


\bibitem{KitFine}
Kit Fine, \cq{Part-whole}, in Barry Smith and 
David Woodruff Smith, \intitle{The Cambridge Companion to Husserl}, 
pp. 463-486.
Cambridge University Press, New York, 1995.


\bibitem{Fauconnier}
Gilled Fauconnier, \cq{Mental Spaces: Aspects of Meaning Construction in Natural Language}.
Cambridge, 1994

\bibitem{Gardenfors}
Peter \Gardenfors{},  
\cq{Does Semantics Need Reality?}.
Riegler A., Peschl M., von Stein A. (eds),
\intitle{Understanding Representation in the Cognitive Sciences.}, 
pages 209-217.
Springer, Boston, MA.

\bibitem{Zenker}
Peter \Gardenfors{} and Frank Zenker,  
\cq{Theory Change as Dimensional Change: Conceptual Spaces 
	Applied to the Dynamics of Empirical Theories}.
\intitle{Synthese 190(6)}, pp. 1039-1058, 2013.  
\biburl{http://lup.lub.lu.se/record/1775234}

\bibitem{GoertzelPLN}
Ben Goertzel, 
\cq{Probabilistic Language Networks:
Integrating Word Grammar and Link Grammar 
in the Framework of Probabilistic Logic}.
\biburl{http://goertzel.org/ProwlGrammar.pdf}

\bibitem{KennethHolmqvist}
Kenneth Holmqvist,
\cq{Conceptual Engineering: Implementing cognitive semantics}, 
in Jens Allwood and Peter \Gardenfors, eds., 
\intitle{Cognitive Semantics}, pp 153 - 171, Amsterdam,
Philadelphia: John Benjamins, 1999.

\bibitem{HolmqvistDiss}
Kenneth Holmqvist, 
\cq{Implementing Cognitive Semantics: Image schemata, 
valence accommodation, and valence suggestion for  
AI and computational linguistics}.
PhD thesis, Dept. of Cognitive Science, Lund University, Lund, Sweden, 1993.

\bibitem{BlackwellPragmatics}
Laurence R. Horn and Gregory Ward, 
\cq{Handbook of Pragmatics}.
Wiley, 2004

\bibitem{Johnson}
Mark Johnson, \cq{The Body in the Mind: 
The Bodily Basis of Meaning, Imagination, and Reason}.  %Chicago, 1990
University of Chicago Press, 1990

\bibitem{MichaelJubien}
Michael Jubien, \cq{Ontology, Modality, and 
the Fallacy of Reference}.  
Cambridge University Press, New York, 1993.

\bibitem{KubotaLevine}
Yusuke Kubota and Robert Levine,
\cq{The syntax-semantics interface of \sq{respective} predication:
A unified analysis in Hybrid Type-Logical Categorial Grammar}
\biburl{https://www.asc.ohio-state.edu/levine.1/publications/kl-resp.pdf}


\bibitem{LakoffJohnson}
George Lakoff and Mark Johnson, 
\cq{Philosophy in the Flesh: the Embodied Mind and its Challenge to Western Thought}.
New York: Basic Books, 1999.


\bibitem{LangackerFoundations}
Ronald Langacker, 
\cq{Foundations of Cognitive Grammar, vol. 1}.  
Stanford University Press, 1991

\bibitem{ZhaohuiLuo}
Zhaohui Luo,
\cq{Type-Theoretical Semantics with Coercive Subtyping}.
\biburl{https://www.cs.rhul.ac.uk/home/zhaohui/ESSLLI11notes.pdf}

\bibitem{ZhaohuiLuoSignatures}
Zhaohui Luo,
\cq{Using Signatures in Type Theory to Represent Situations}.
\biburl{https://www.researchgate.net/publication/268079019_Using_Signatures_in_Type_Theory_to_Represent_Situations}


\bibitem{LuoSoloviev}
Zhaohui Luo and Sergei Soloviev,
\cq{Dependent Coercions}.
\biburl{https://www.sciencedirect.com/science/article/pii/S1571066105803147}

\bibitem{MeryMootRetore}
Bruno Mery, Richard Moot, and Christian Retor\'e, \cq{
	Plurals: Individuals and sets
	in a richly typed semantics}.  
\biburl{http://arxiv.org/pdf/1401.0660.pdf} \archiveDate{3 Jan 2014}

\bibitem{ErwanMoreau}
Erwan Moreau,
\cq{From link grammars to categorial grammars}
\biburl{https://hal.archives-ouvertes.fr/hal-00487053/document}


\bibitem{OsborneMaxwell}
Timothy Osborne and Daniel Maxwell, 
\cq{A Historical Overview of the Status of Function
Words in Dependency Grammar}
\biburl{https://www.aclweb.org/anthology/W15-2127}


\bibitem{EstherPascual}
Esther Pascual, 
\cq{Fictive Interaction: The conversation frame in thought, language, and discourse}.
Philadelphia, John Benjamins, 2014.

\bibitem{EfePeker}
Efe Peker,
\cq{Following 9/11: George W. Bush's Discursive Re-Articulation of American Social Identity}
Master's Dissertation, Link\"oping University, Sweden
\biburl{http://www.diva-portal.org/smash/get/diva2:21407/FULLTEXT01.pdf}

\bibitem{PetitotSyntaxe}
Jean Petitot, \cq{Syntax Topologique et Grammaire Cognitive}.
\intitle{Langages 25.103}, pp. 97-128, 1991. 

%?
\bibitem{JeanPetitot}
Jean Petitot, \cq{The morphodynamical turn of cognitive linguistics}.
\biburl{https://journals.openedition.org/signata/549}

\bibitem{Pinker}
Steven Pinker, \cq{The Stuff of Thought: Language As a Window Into Human Nature}.
Penguin, 2007.  

\bibitem{JamesPustejovsky}
James Pustejovsky, 
\cq{A Survey of Dot Objects}
Unpublished manuscript, 2006.

\bibitem{Ramstead}
Maxwell James Ramstead, 
\cq{Transcendental Phenomenology and Naturalistic Epistemology.}
\biburl{https://archipel.uqam.ca/8209/1/M14029.pdf}

\bibitem{SivaReddy}
Siva Reddy, \i{et. al},
\cq{Transforming Dependency Structures to Logical Forms for Semantic Parsing.}
\biburl{https://aclweb.org/anthology/Q16-1010}

\bibitem{TerryRegier}
Terry Regier, 
\i{The Human Semantic Potential: 
Spatial Language and Constrained Connectionism}.
Cambridge, MA: MIT Press, 2014.

\bibitem{Rossi}
\Aurelie{} Rossi, \cq{Applicative and Combinatory Categorial Grammar:
	Analysis of the French Interrogative Sentences}.
\intitle{FLAIRS Conference, Association for the Advancement of Artificial
Intelligence}, 2008.
\biburl{https://www.aaai.org/Papers/FLAIRS/2008/FLAIRS08-118.pdf}

\bibitem{Schneider}
Gerold Schneider, 
\cq{A Linguistic Comparison of Constituency, Dependency and Link Grammar}.
Zurich University, diploma, 2008.
\biburl{https://files.ifi.uzh.ch/cl/gschneid/papers/FINALSgeroldschneider-latl.pdf}


\bibitem{MattSelway}
Matt Selway, \i{et. al},
\cq{Configuring Domain Knowledge for Natural Language Understanding}
\biburl{http://ceur-ws.org/Vol-1128/paper9.pdf}


\bibitem{SleatorTamperley}
Daniel D. Sleator and Davy Tamperley, 
\cq{Parsing English with a Link Grammar}.
\biburl{https://www.link.cs.cmu.edu/link/ftp-site/link-grammar/LG-IWPT93.pdf}

\bibitem{DavidWoodruffSmith}
David Woodruff Smith,
\cq{Mind World}.  Cambridge University Press, 2004.

\bibitem{KiyoshiSudo}
Kiyoshi Sudo, \i{et. al.},
\cq{An Improved Extraction Pattern Representation Model
for Automatic IE Pattern Acquisition}
\biburl{https://www.aclweb.org/anthology/P03-1029}


\bibitem{TanakaEtAl}
Ribeka Tanaka, \i{et. al.}, \cq{Factivity and Presupposition
in Dependent Type Semantics}
\biburl{http://www.lirmm.fr/tytles/Articles/Tanaka.pdf}

\bibitem{OrlinVakarelov}
Orlin Vakarelov,
\cq{Pre-cognitive Semantic Information}.
\biburl{https://link.springer.com/article/10.1007/s12130-010-9109-5}

\bibitem{VakarelovAgent}
Orlin Vakarelov, 
\cq{The cognitive agent: Overcoming
informational limits}
\biburl{https://philarchive.org/archive/VAKTCAv1}


\bibitem{JanVanEijck}
Jan van Eijck, 
\cq{Dynamic Reasoning Without Variables}
\biburl{https://www.semanticscholar.org/paper/Dynamic-Reasoning-Without-EijckCWI/4fb3b23f81b8691fbdaf8d3eb24c086c5f826954}

Rik van Noord
\bibitem{RikVanNoord}
Rik van Noord, \i{et. al.},
\cq{Exploring Neural Methods for Parsing Discourse Representation Structures}
\biburl{https://www.aclweb.org/anthology/Q18-1043}


\bibitem{AnneVilnat}
Anne Vilnat,
\cq{Dialogue et analyse de phrases}
Habilitation M\'emoire, Universit\'e Paris-Sud  
\biburl{https://perso.limsi.fr/anne/HDR/MemoireHDR.pdf}

%\bibitem{WiegandMereology}
\bibitem{OlavKWiegand}
Olav K. Wiegand, 
\cq{A Formalism Supplementing Cognitive Semantics Based on a New Approach to Mereology}.
Ingvar Johansson, Bertin Klein and Thomas Roth-Berghofer, eds.,  
\intitle{Contributions to the Third International Workshop on Philosophy and Informatics}, 2006. 

\bibitem{WiegandGestalts}
\underlines
\cq{On referring to Gestalts}.
Mirja Hartimo, ed., \intitle{Phenomenology and Mathematics}, pp. 183-211.  Springer, 2010. 

\bibitem{Wille}
Rudolf Wille, 
\cq{Conceptual Graphs and Formal Concept Analysis}.
\intitle{Conceptual Structures: Fulfilling Peirce's Dream
Fifth International Conference on Conceptual Structures}, 1997.

\bibitem{YiyuYao}
Yiyu Yao, 
\cq{A Comparative Study of Formal Concept
	Analysis and Rough Set Theory in Data Analysis}.
\biburl{http://www2.cs.uregina.ca/~yyao/PAPERS/Rough_concept.pdf}

\bibitem{JordanZlatev}
Jordan Zlatev, 
%\underlines
\cq{The Dependence of Language on Consciousness}.
\biburl{http://www.mrtc.mdh.se/~gdc01/work/ARTICLES/2014/4-IACAP\%202014/IACAP14-GDC/pdf/Language-Consciousness-Zlatev.pdf}


}
\end{thebibliography}
