


\begin{thebibliography}{99}
\phantomsection \label{References}
\addcontentsline{toc}{section}{References}
{\fontfamily{lmtt}\selectfont\scriptsize



\bibitem{AbadiCardelliUntyped}{%
Mart\'{\OldI}n Abadi and Luca Cardelli,
\cq{A Semantics of Object Types}.  % 
Proceedings of the IEEE Symposium on Logic in Computer Science, 
Paris, 1994.
\biburl{http://lucacardelli.name/Papers/PrimObjSemLICS.A4.pdf}}


\bibitem{AbadiCardelli}
\_\_\_\_\_
\cq{A Theory of Primitive Objects: 
Untyped and First-Order Systems}
\biburl{http://lucacardelli.name/Papers/PrimObj1stOrder.pdf}


\bibitem{AsudehGiorgolo}
Ash Asudeh and Gianluca Giorgolo,  
\bibtitle{Enriched Meanings: Natural Language Semantics with Category Theory}.
Oxford, 2020. 


\bibitem{AsherLuo}
Nicholas Asher and Zhaohui Luo,  
\cq{Formalization of Coercions in Lexical Semantics}.
\biburl{https://semanticsarchive.net/sub2012/AsherZhaoHui.pdf}


\bibitem{JerryTBall}
Jerry T. Ball,  
\cq{Double R Grammar: The Grammatical 
Encoding of Referential and Relational Meaning in
English}.
\biburl{https://citeseerx.ist.psu.edu/document?repid=rep1&type=pdf&doi=34c258564f72b6dc6455aeaac6e6be1a4a07d262}


\bibitem{BarkerShan}
Chris Barker and Chung-chieh Shan,  
\bibtitle{Continuations and Natural Language}.
Oxford, 2014. 


\bibitem{LawrenceWBarsalou}
Lawrence W. Barsalou,  
\cq{Grounded Cognition}.
\biburl{http://matt.colorado.edu/teaching/highcog/spr10/readings/b8.pdf}



\bibitem{BastKorzen}
Hannah Bast and Claudius Korzen,  
\cq{A Benchmark and Evaluation for Text Extraction from PDF}.
\biburl{https://ad-publications.cs.uni-freiburg.de/benchmark.pdf}



\bibitem{HansCBoas}
Hans C. Boas, 
\cq{Cognitive Construction Grammar}.
\biburl{https://sites.la.utexas.edu/hcb/files/2011/02/CCxG-October22-2010.pdf}


\bibitem{GregCarlson}
Greg Carlson,
\cq{Thematic Roles and the Individuation of Events}
\biburl{https://www.sas.rochester.edu/lin/people/faculty/carlson_greg/assets/pdf/them-roles-events.pdf}


\bibitem{LucasChampollionC}
Lucas Champollion,
\cq{Covert Distributivity in Algebraic Event Semantics}
\intitle{Semantics \& Pragmatics}, Volume 9 (2016), pages 1-65. 
\biburl{https://semprag.org/article/view/sp.9.15}


\bibitem{ChampollionDissertation}
\_\_\_\_\_,
\cq{Parts of a Whole: Distributivity as a Bridge Between Aspect and Measurement}
Dissertation, University of Pennsylvania, 2010.
\biburl{https://repository.upenn.edu/cgi/viewcontent.cgi?article=2117&context=edissertations}



\bibitem{RobinCooper}
Robin Cooper,
\cq{Perception, Types and Frames}
\biburl{https://link.springer.com/chapter/10.1007/978-3-030-50200-3_8}


\bibitem{CopleyHarley}
Bridget Copley and Heidi Harley,
\cq{A Force-Theoretic Framework for Event Structure}
\biburl{http://heidiharley.com/heidiharley/wp-content/uploads/2016/09/CopleyAndHarley2015Published.pdf}






\bibitem{DeWitBrisard}
Astrid De Wit and Frank Brisard,
\cq{A Cognitive Grammar Account of the Semantics of the English Present Progressive}
\biburl{https://www.researchgate.net/publication/326960775_Nominal_Grounding_Elements_in_English_A_Domain-based_Account}



\bibitem{MattDuckham}
Matt Duckham,
\cq{Object Calculus and the Object-Oriented Analysis
and Design of an Error-Sensitive GIS}
\biburl{http://www.geosensor.net/papers/oo.pdf}


\bibitem{DuziFait}
Marie Du\v{z}\i{\OldI} and Michal Fait,
\cq{Integrating Special Rules Rooted in Natural Language Semantics into
the System of Natural Deduction}
\biburl{https://www.scitepress.org/Papers/2020/93696/93696.pdf}



\bibitem{EisnerSmith}
Jason Eisner and Noah A. Smith,
\cq{Favor Short Dependencies: Parsing with Soft
and Hard Constraints on Dependency Length}
\biburl{https://www.cs.jhu.edu/~jason/papers/eisner+smith.iwptbook10.pdf}



\bibitem{GildeaTemperley}
Daniel Gildea and David Temperley,
\cq{Optimizing Grammars for Minimum Dependency Length}
\biburl{https://www.cs.rochester.edu/~gildea/pubs/gildea-temperley-acl07.pdf}



\bibitem{HongEisner}
Juneki Hong and Jason Eisner,
\cq{Deriving Multi-Headed Planar Dependency Parses
from Link Grammar Parses}.
\biburl{https://www.cs.jhu.edu/~jason/papers/hong+eisner.tlt14.paper.pdf}



\bibitem{MullerWechsler}
Stefan M\"uller and Stephen Wechsler,
\cq{Lexical Approaches to Argument Structure}
\biburl{https://hpsg.hu-berlin.de/~stefan/Pub/arg-st.pdf}



\bibitem{MustafaFatah}
Kobeen Raouf Mustafa and Azad Hasan Fatah,
\cq{Nominal Grounding Elements in English:
A Domain-based Account}
\biburl{https://www.researchgate.net/publication/326960775_Nominal_Grounding_Elements_in_English_A_Domain-based_Account}


\bibitem{JeanMarkGawron}
Jean Mark Gawron,
\cq{Circumstances and Perspective:
The Logic of Argument Structure}
\biburl{https://escholarship.org/content/qt7sd5987t/qt7sd5987t_noSplash_14d78590a8657a71ed9ad46dc6e69064.pdf}


\bibitem{JeanMarkGawronPaths}
\_\_\_\_\_,
\cq{Paths and the Language of Change}
\biburl{https://gawron.sdsu.edu/paths_change.pdf}


\bibitem{ChrisGenovesi}
Chris Genovesi,
\cq{Metaphor and What is Meant: Metaphorical content, what is
said, and contextualism}
\biburl{https://www.tcd.ie/slscs/assets/documents/Clinical-speech/genovesi_2019_metaphor.pdf}



\bibitem{RodriguezCancho}
Carlos G\'omez-Rodr\'{\OldI}guez and Ramon Ferrer-i-Cancho
\cq{The Scarcity of Crossing Dependencies: a direct outcome of a specific
constraint?}
\biburl{https://arxiv.org/pdf/1601.03210.pdf}



\bibitem{AndrewDGordon}
Andrew D. Gordon, \i{et. al.},
\cq{Compilation and Equivalence of Imperative Objects}
\biburl{https://www.microsoft.com/en-us/research/wp-content/uploads/1997/01/maya.pdf}



\bibitem{SergioGuadarrama}
Sergio Guadarrama, \i{et. al.},
\cq{Grounding Spatial Relations for Human-Robot Interaction}
\biburl{https://citeseerx.ist.psu.edu/document?repid=rep1&type=pdf&doi=e64fd4eb33199fc2cc731aec1c25d4e88a4d4f40}



\bibitem{RobertFHadley}
Robert F. Hadley,
\cq{A Default-Oriented Theory of
Procedural Semantics}
\biburl{https://onlinelibrary.wiley.com/doi/pdf/10.1207/s15516709cog1301_4}


\bibitem{DanielWHarris}
Daniel W. Harris,
\cq{Speech Act Theoretic Semantics}.
Dissertation, CUNY, 2014.
\biburl{https://academicworks.cuny.edu/cgi/viewcontent.cgi?article=1221&context=gc_etds}


\bibitem{ManjulaUdayangaHemapala}
Manjula Udayanga Hemapala,
\cq{Robots for Humanitarian Demining}.
\biburl{https://cdn.intechopen.com/pdfs/56656.pdf}


\bibitem{PadraigHiggins}
Padraig Higgins, \i{et. al.}, 
\cq{Towards Making Virtual Human-Robot Interaction a Reality}
\biburl{https://iral.cs.umbc.edu/Pubs/VAMHRI2021-Higgins.pdf}



\bibitem{DarrinLouisHindsill}
Darrin Louis Hindsill,
\cq{Its a Process \i{and} an Event:
Perspectives in event semantics}.
Dissertation, University of Amsterdam, 2007.
\biburl{https://eprints.illc.uva.nl/id/eprint/2058/1/DS-2007-03.text.pdf}



\bibitem{HoWang}
Seng-Beng Ho and Zhaoxia Wang,
\cq{Language and Robotics: Complex Sentence Understanding}.
\biburl{https://ink.library.smu.edu.sg/cgi/viewcontent.cgi?article=6486&context=sis_research}






\bibitem{KennethHolmqvist}
Kenneth Holmqvist,
\cq{Conceptual Engineering: Implementing cognitive semantics}, 
in Jens Allwood and Peter \Gardenfors, eds., 
\intitle{Cognitive Semantics}, pp 153 - 171, Amsterdam,
Philadelphia: John Benjamins, 1999.

\bibitem{KennethHolmqvistDissertation}
Kenneth Holmqvist, 
\cq{Implementing Cognitive Semantics: Image schemata, 
valence accommodation, and valence suggestion for  
AI and computational linguistics}.
PhD thesis, Dept. 


\bibitem{HornPeirce}
Laurence R. Horn and Istvan Keckes Peirce,
\cq{Pragmatics, Discourse, and Cognition}
\biburl{http://www.albany.edu/faculty/ikecskes/files/Horn\%20and\%20Kecskes\%2065-45-R1026-Horn.pdf}


\bibitem{YueHu}
Yue Hu, \i{et. al.},
\cq{Towards Active Physical Human-Robot Interaction:
quantifying the human state during interactions}
\biburl{https://hal.archives-ouvertes.fr/hal-03567276/document}


\bibitem{RadhaJagadeesan}
Radha Jagadeesan, \i{et. al.},
\cq{Monotonic Typestates for the Object Calculus}
\biburl{https://fpl.cs.depaul.edu/jriely/papers/2009-monotone.pdf}


\bibitem{KyleJohnson}
Kyle Johnson,
\cq{What Makes a Theta-role}
\biburl{https://www.qmul.ac.uk/sllf/media/sllf-new/department-of-linguistics/hagit-borer-celebration/Johnson.pdf}


\bibitem{MarkJohnson}
Mark Johnson, \cq{The Body in the Mind: 
The Bodily Basis of Meaning, Imagination, and Reason}.
University of Chicago Press, 1990


\bibitem{WernerKallmeyer}
Werner Kallmeyer,
\cq{Verbal Practices of Perspective Grounding}
\biburl{https://d-nb.info/120819738X/34}



\bibitem{AndreyKurenkov}
Andrey Kurenkov, \i{et. al.},
\cq{An Evaluation of GUI and Kinesthetic Teaching Methods for
Constrained-Keyframe Skills}
\biburl{https://www.sim.ece.utexas.edu/static/papers/kurenkov_iros2015.pdf}





\bibitem{LakoffJohnson}
George Lakoff and Mark Johnson, 
\bibtitle{Philosophy in the Flesh: the Embodied Mind and its Challenge to Western Thought}.
New York: Basic Books, 1999.


\bibitem{LakoffJohnsonMetaphors}
George Lakoff and Mark Johnson, 
\bibtitle{Metaphors We Live By}.
University of Chicago, 1980.


\bibitem{LangackerIntro}
Ronald Langacker, 
\bibtitle{Cognitive Grammar: A Basic Introduction}.  
Oxford, 2008.

\bibitem{LangackerCCxG}
Ronald Langacker, 
\cq{Cognitive (Construction) Grammar}.  
\biburl{https://www.degruyter.com/document/doi/10.1515/COGL.2009.010/html?lang=en}


\bibitem{LangackerConstructions}
\_\_\_\_\_, 
\cq{Constructions in Cognitive Grammar}.  
\biburl{https://www.jstage.jst.go.jp/article/elsj1984/20/1/20_1_41/_pdf/-char/en}

\bibitem{LangackerConceptualization}
\_\_\_\_\_, 
\bibtitle{Grammar and Conceptualization} 
de Gruyter, 1999). 

\bibitem{LangackerClause}
\_\_\_\_\_, 
\cq{How to Build and English Clause}.  
\biburl{https://oaji.net/articles/2016/3124-1458506162.pdf}


\bibitem{LangackerEvidentiality}
\_\_\_\_\_, 
\cq{Evidentiality in Cognitive Grammar}.  
\biburl{https://benjamins.com/catalog/pbns.271.02lan}


\bibitem{LangackerPresent}
\_\_\_\_\_, 
\cq{The English Present: 
Temporal coincidence vs. epistemic immediacy}.  
\biburl{https://benjamins.com/catalog/hcp.29.06lan}


\bibitem{LebaniLenci}
Gianluca E. Lebani and Alessandro Lenci,
\cq{A Distributional Model of Verb-Specific
Semantic Roles Inferences}
\biburl{https://colinglab.humnet.unipi.it/wp-content/uploads/2012/12/Lebani-Lenci-2018.pdf}


\bibitem{JosephLehmann}
Joseph Lehmann, \i{et. al.},
\cq{Age-Related Hearing Loss, Speech 
Understanding and Cognitive Technologies}.
\biburl{https://link.springer.com/article/10.1007/s10772-021-09817-z}




\bibitem{SanderLestrade}
Sander Lestrade, 
\cq{The Space of Case}.
\biburl{https://repository.ubn.ru.nl/bitstream/handle/2066/82611/82611.pdf?sequence=1&isAllowed=y}


\bibitem{GiacomoLunghi}
Giacomo Lunghi, \i{et. al.},
\cq{An Advanced, Adaptive and Multimodal Graphical User Interface for
Human-robot Teleoperation in Radioactive Scenarios}.
\biburl{https://www.scitepress.org/Papers/2016/59714/59714.pdf}



\bibitem{GiacomoLunghiMultimodal}
Giacomo Lunghi, \i{et. al.},
\cq{Multimodal Human-Robot Interface for
Accessible Remote Robotic Interventions
in Hazardous Environments}.
\biburl{https://cds.cern.ch/record/2699858/files/untitled.pdf}





\bibitem{ClaudiaMaienborn}
Claudia Maienborn,
\cq{Event Semantics}.
\biburl{https://www.researchgate.net/publication/236898346_Event_semantics}



\bibitem{RyanMcDonald}
Ryan McDonald, \i{et. al.},
\cq{Non-projective Dependency Parsing using Spanning Tree Algorithms}.
\biburl{https://ryanmcd.github.io/papers/nonprojectiveHLT-EMNLP2005.pdf}



\bibitem{MelanieMitchell}
Melanie Mitchell,
\bibtitle{Artificial Intelligence: A Guide for Thinking Humans}.
Macmillan, 2019.


\bibitem{ErwanMoreau}
Erwan Moreau,
\cq{From Link Grammars to Categorial Grammars}
\biburl{https://hal.archives-ouvertes.fr/hal-00487053/document}


\bibitem{NeusteinChristen}
Amy Neustein and Nathaniel Christen, 
\bibtitle{Covid, Cancer, and Cardiac Care}. Elsevier, 2022. 


\bibitem{AnaCristinaRamadaPaiva}
Ana Cristina Ramada Paiva,  
\cq{Automated Specification-Based Testing of
Graphical User Interfaces}.
Dissertation, University of Porto, 2006.
\biburl{https://web.fe.up.pt/~apaiva/PhD/PhDGUITesting.pdf}


\bibitem{PeterPelyvas}
P\'eter Pelyv\'as, 
\cq{Epistemic Modality: A choice 
between alternative cognitive models}.
\biburl{https://litere.uvt.ro/publicatii/BAS/pdf/no/bas_2011_articles/22\%20247-259.pdf}


\bibitem{PeterPelyvasDeontic}
\_\_\_\_\_, 
\cq{On Epistemic and Deontic Grounding}.
\biburl{https://argumentum.unideb.hu/2019-anyagok/special_issue_I/pelyvasp.pdf}


\bibitem{PeterPelyvasDevelopment}
\_\_\_\_\_, 
\cq{The Development of the Grounding Predication: Epistemic Modals and Cognitive Predicates}.
\biburl{https://brill.com/display/book/9780585474267/B9780585474267_s010.xml}


\bibitem{JeanPetitot}
Jean Petitot, \cq{The Morphodynamical Turn of Cognitive Linguistics}.
\biburl{https://journals.openedition.org/signata/549}


\bibitem{PetitotDoursat}
Jean Petitot and Ren\'e Doursat, 
\bibtitle{Cognitive Morphodynamics:
Dynamical Morphological Models of Constituency in Perception and Syntax}.
Peter Lang, 2011


\bibitem{EmilyPitler}
Emily Pitler, 
\bibtitle{Models for Improved Tractability and Accuracy in Dependency acy in Dependency Parsing}.
Dissertation, University of Pennsylvania, 2013.
\biburl{https://repository.upenn.edu/cgi/viewcontent.cgi?article=2070&context=edissertations}.



\bibitem{JamesPustejovsky}
James Pustejovsky, 
\cq{The Syntax of Event Structure}.
\biburl{https://www.cs.rochester.edu/u/james/Papers/Pustejovsky-event-structure.pdf}.



\bibitem{SzafirSzafir}
Daniel Szafir and Danielle Albers Szafir, 
\cq{Connecting Human-Robot Interaction and Data Visualization}.
\biburl{https://cu-visualab.org/papers/vis_hri_final_acc.pdf}.





\bibitem{ShimEpstein}
Jae-Young Shim and Samuel David Epstein,
\cq{Two Notes on Possible Approaches
to the Unification of Theta Relations}
\biburl{https://jaeyoungshim.weebly.com/uploads/1/2/3/1/12312623/linguistic_analysis_two_notes_jae-young_shim.pdf}


\bibitem{GeroldSchneider}
Gerold Schneider, 
\cq{A Linguistic Comparison of Constituency, Dependency and Link Grammar}.
Zurich University, Diploma, 2008.%
\hspace{-.6em}\biburl{https://files.ifi.uzh.ch/cl/gschneid/papers/FINALSgeroldschneider-latl.pdf}



\bibitem{SleatorTamperley}
Daniel D. Sleator and Davy Tamperley, 
\cq{Parsing English with a Link Grammar}.
\biburl{https://www.link.cs.cmu.edu/link/ftp-site/link-grammar/LG-IWPT93.pdf}


\bibitem{MichaelSprangerIncremental}
Michael Spranger, 
\cq{Incremental Grounded Language Learning in
Robot-Robot Interactions}.
\biburl{http://www2.ece.rochester.edu/projects/rail/mlhrc2015/papers/mlhrc-rss15-spranger.pdf}



\bibitem{MichaelSprangerRobots}
Michael Spranger, 
\cq{Procedural Semantics for Autonomous Robots -- A Case Study in
Locative Spatial Language}.
\biburl{https://www.researchgate.net/publication/280830547_Procedural_Semantics_for_Autonomous_Robots_-_A_Case_Study_in_Locative_Spatial_Language}



\bibitem{MichaelSprangerEvolution}
\_\_\_\_\_, 
\cq{The Evolution of Grounded Spatial Language}.
\biburl{https://langsci-press.org/catalog/book/53}


\bibitem{MichaelSpranger}
Michael Spranger, \i{et. al,},
\cq{Open-ended Procedural Semantics}.
\biburl{https://martin-loetzsch.de/publications/spranger12openended.pdf}





\bibitem{SteffensenFill}
Sune Vork Steffensen and Alwin Fill,
\cq{Ecolinguistics: The state of the art and future horizons}
\biburl{https://findresearcher.sdu.dk/ws/files/87218550/Steffensen_2014_Language_Sciences.pdf}



\bibitem{StefanieTellex}
Stefanie Tellex, \i{et. al.},
\cq{Robots That Use Language: A Survey}
\biburl{https://h2r.cs.brown.edu/wp-content/uploads/tellex20.pdf}



\bibitem{LiuZhang}
Rui Liu and Xiaoli Zhang,
\cq{A Review of Methodologies for NaturalLanguage-Facilitated Human-Robot Cooperation}
\biburl{https://arxiv.org/pdf/1701.08756.pdf}



\bibitem{CynthiaMatuszek}
Cynthia Matuszek, \i{et. al.},
\cq{Learning to Parse Natural Language Commands
to a Robot Control System}
\biburl{https://homes.cs.washington.edu/~lsz/papers/mhzf-iser12.pdf}


\bibitem{ChukwualukaMichaelUyanne}
Chukwualuka Michael Uyanne, \i{et. al.},
\cq{Ecolinguistic Perspective: Dialectics of Language
and Environment}
\biburl{https://ezenwaohaetorc.org/journals/index.php/ajells/article/viewFile/5-1-2014-010/61}





\bibitem{OrlinVakarelov}
Orlin Vakarelov,
\cq{Pre-cognitive Semantic Information}.
\biburl{https://link.springer.com/article/10.1007/s12130-010-9109-5}

\bibitem{VakarelovAgent}
\_\_\_\_\_, 
\cq{The Cognitive Agent: Overcoming
informational limits}
\biburl{https://philarchive.org/archive/VAKTCAv1}


\bibitem{VepstasGoertzel}
Linas Vepstas and Ben Goertzel, 
\cq{Learning Language from a Large (Unannotated) Corpus}
\biburl{https://arxiv.org/pdf/1401.3372.pdf}


\bibitem{LucyLuWang}
Lucy Lu Wang, \i{et al.}, 
\cq{CORD-19: The Covid-19 Open Research Dataset}.
\bibtitle{ArXiv}, 2020. 
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7251955}



\bibitem{AlexanderWilkinson}
Alexander Wilkinson, \i{et al.}, 
\cq{Design guidelines for human–robot interaction
with assistive robot manipulation systems}.
\biburl{https://www.degruyter.com/document/doi/10.1515/pjbr-2021-0023/html?lang=en}



\bibitem{PerathamWiriyathammabhum}
Peratham Wiriyathammabhum, 
\cq{Computer Vision and Natural Language Processing:
Recent Approaches in Multimedia and Robotics}
\biburl{https://www-hlb.cs.umd.edu/sites/default/files/scholarly_papers/PerathamW.pdf}



\bibitem{HimanshuYadav}
Himanshu Yadav, \i{et. al.}, 
\cq{Are Formal Restrictions on Crossing Dependencies Epiphenomenal?}
\biburl{http://socsci.uci.edu/~rfutrell/papers/yadav2019formal.pdf}


\bibitem{YadavDarlington}
Poonam Yadav and John Darlington, 
\cq{Conceptual Frameworks for Building Online Citizen Science Projects}
\biburl{https://hcjournal.org/index.php/jhc/article/view/72}



\bibitem{YancoDrury}
Holly A. Yanco and Jill Drury, 
\cq{Classifying Human-Robot Interaction:
An Updated Taxonomy}
\biburl{https://www.sci.brooklyn.cuny.edu/~sklar/teaching/f06/air/papers/yanco-drury-tax-smc04.pdf}



\bibitem{JordanZlatev}
Jordan Zlatev, 
\cq{Embodiment, Language, and Mimesis}
\biburl{https://lucris.lub.lu.se/ws/portalfiles/portal/4514085/1044802.pdf}


\bibitem{JordanZlatevPhenomenology}
\_\_\_\_\_, 
\cq{Phenomenology and Cognitive Linguistics}
\biburl{https://citeseerx.ist.psu.edu/document?repid=rep1&type=pdf&doi=ebc99d9442497d36be7477f393dcc38d2d53ab5b}


}
\end{thebibliography}






