\begin{thebibliography}{99}
\phantomsection \label{References}
\addcontentsline{toc}{section}{References}
{\fontfamily{lmtt}\selectfont\scriptsize


\makeatletter
\g@addto@macro{\UrlBreaks}{\UrlOrds}
\makeatother

\bibitem{AhlawatSah}
Joginder Ahlawat and Saurabh Kumar Sah, 
\cq{Optimal Drinking Water Distribution System Designing using Network
Analysis and Geospatial Technology}.
\biburl{https://globaljournals.org/GJHSS_Volume17/5-Optimal-Drinking-Water-Distribution.pdf}



\bibitem{RenzoAngles}
Renzo Angles, \i{et. al.}, 
\cq{Foundations of Modern Query Languages for Graph
Databases}.
\biburl{http://renzoangles.net/files/csur2017.pdf}



\bibitem{JeroenBach}
Jeroen Bach, 
\cq{Theory and Experimental Evaluation of Object-
Relational Mapping Optimization Techniques: 
How to ORM and how not to ORM}.
Thesis, University of Amsterdam, 2010.
\biburl{https://homepages.cwi.nl/~jurgenv/theses/JeroenBach.pdf}


\bibitem{JeffreyMBarnes}
Jeffrey M. Barnes, 
\cq{Object-Relational Mapping as a Persistence
Mechanism for Object-Oriented Applications}.
\biburl{https://digitalcommons.macalester.edu/cgi/viewcontent.cgi?article=1006&context=mathcs_honors}


\bibitem{RenildeBecque}
Renilde Becqu\'e, 
\cq{Accelerating Building Decarbonization: Eight attainable policy 
pathways to net zero for all}.
\biburl{https://wrirosscities.org/sites/default/files/19_WP_ZCB_final.pdf}


\bibitem{JundeChen}
Junde Chen, \i{et. al.},
\cq{Intelligent Monitoring Method of Water Quality
Based on Image Processing and RVFL-GMDH Model}.
\biburl{https://ietresearch.onlinelibrary.wiley.com/doi/full/10.1049/iet-ipr.2020.0254}


\bibitem{ChenLee}
Jeang-Kuo Chen and Wei-Zhe Lee,
\cq{An Introduction of NoSQL Databases Based on Their
Categories and Application Industries}.
\biburl{https://mdpi-res.com/d_attachment/algorithms/algorithms-12-00106/article_deploy/algorithms-12-00106-v2.pdf?version=1559011753}


\bibitem{PierreEvaristeDagand}
Pierre-\'Evariste Dagand,
\cq{A Cosmology of Datatypes: 
Reusability and Dependent Types}.
Dissertation, University of Strathclyde, 2013
\biburl{https://citeseerx.ist.psu.edu/document?type=pdf&doi=1997710cea4b67b9e53df96d6dee7f2c3e5c5556}


\bibitem{MartinFowler}
Martin Fowler,
\bibtitle{Patterns of Enterprise Application Architecture}.
Addison-Wesley, 2002
\biburl{https://www.martinfowler.com/books/eaa.html}


\bibitem{JanHidders}
Jan Hidders,
\cq{Typing Graph-Manipulation Operations}
\biburl{http://adrem.uantwerpen.be/bibrem/pubs/hidders.3.pdf}


\bibitem{ThomasHies}
Thomas Hies, \i{et. al.},
\cq{Enhanced Water-Level Detection by Image Processing}
\biburl{https://www.researchgate.net/publication/262337135_Enhanced_water-level_detection_by_image_processing}




\bibitem{RafaelHorn}
Rafael Horn, \i{et. al.},
\cq{The BIM2LCA Approach: An Industry Foundation
Classes (IFC)-Based Interface to Integrate Life Cycle
Assessment in Integral Planning}
\biburl{https://www.mdpi.com/2071-1050/12/16/6558/pdf-vor}



\bibitem{ShaunHowell}
Shaun Howell, \i{et. al.},
\cq{Integrating Building and Urban Semantics to Empower Smart
Water Solutions}
\biburl{https://www.sciencedirect.com/science/article/pii/S0926580517301759}



\bibitem{BartJacobs}
Bart Jacobs,
\bibtitle{Categorical Logic and Type Theory}.
Elsevier, 2001.



\bibitem{IrelandBowers}
Christopher Ireland and David Bowers,
\cq{Exposing the Myth: Object-Relational Impedance Mismatch is a Wicked Problem}
\biburl{https://oro.open.ac.uk/43318/1/download.php_articleid\%3Ddbkda_2015_2_10_50020}



\bibitem{DavidAClunie}
David A. Clunie, 
\cq{DICOM Structured Reporting}.
\biburl{http://www.dclunie.com/pixelmed/DICOMSR.book.pdf}



\bibitem{SamiyaKhan}
Samiya Khan, \i{et. al.},
\cq{Storage Solutions for Big Data Systems: A Qualitative Study
and Comparison}.
\biburl{https://arxiv.org/pdf/1904.11498.pdf}

\bibitem{JulianKeil}
Julian Keil, \i{et. al.},
\cq{Preparing the HoloLens for user Studies: an Augmented Reality
Interface for the Spatial Adjustment of Holographic Objects in 3D
Indoor Environments}.
\biburl{https://d-nb.info/1208303023/34}


\bibitem{PraveenKumar}
Praveen Kumar, \i{et. al.},
\bibtitle{Hydroinformatics: Data Integrative Approaches in Computation, Analysis, and Modeling}.
Taylor \& Francis, 2019.
\biburl{https://vdoc.pub/download/hydroinformatics-data-integrative-approaches-in-computation-analysis-and-modeling-1thfcnva63kg}


\bibitem{MBLuther}
M. B. Luther,  \i{et. al.},
\cq{A simple-to-use calculator for determining the total
solar heat gain of a glazing system}.
\biburl{https://anzasca.net/wp-content/uploads/2014/08/p511.pdf}




\bibitem{DivyaMahajan}
Divya Mahajan, \i{et. al.},
\cq{Improving the Energy Efficiency of Relational and
NoSQL Databases via Query Optimizations}.
\biburl{https://www.sciencedirect.com/science/article/pii/S2210537918301112}


\bibitem{MikeMarti}
Mike Marti, 
\cq{Translating Between Graph
Database Query Languages}.
Thesis, ETH Z\"urich, 2022. 
\biburl{https://www.research-collection.ethz.ch/bitstream/handle/20.500.11850/575738/1/Marti_Mike.pdf}


\bibitem{WimMartens}
Wim Martens, \i{et. al.},
\cq{Representing Paths in Graph Database Paern Matching}.
\biburl{https://arxiv.org/pdf/2207.13541.pdf}



\bibitem{MolnarBenczur}
B\'alint Moln\'ar and Andr\'as Bencz\'ur,
\cq{The Application of Directed Hyper-Graphs for Analysis of
Models of Information Systems}.
\biburl{https://www.mdpi.com/2227-7390/10/5/759}


\bibitem{LedvinkaKremen}
Martin Ledvinka and Petr K\v{r}emen,
\cq{Formalizing Object-ontological Mapping Using
F-logic}.
\biburl{https://kbss.felk.cvut.cz/reports/2019/19ruleml-report.pdf}


\bibitem{LattnerAdve}
Chris Lattner and Vikram Adve,
\cq{LLVM: A Compilation Framework for
Lifelong Program Analysis \& Transformation}.
\biburl{https://llvm.org/pubs/2004-01-30-CGO-LLVM.pdf}


\bibitem{TommiLaukkanen}
Tommi Laukkanen, \i{et. al.},
\cq{Virtual technologies in supporting sustainable consumption: From a
single-sensory stimulus to a multi-sensory experience}.
\biburl{https://e-tarjome.com/storage/panel/fileuploads/2022-06-27/1656317001_e16754.pdf}



\bibitem{LedvinkaKremenComparison}
Martin Ledvinka and Petr K\v{r}emen,
\cq{A Comparison of Object-Triple Mapping
Frameworks}.
\biburl{https://www.semantic-web-journal.net/system/files/swj1910.pdf}



\bibitem{DanielMartin}
Daniel Martin, \i{et. al.},
\cq{Multimodality in VR: A survey}.
\biburl{https://arxiv.org/pdf/2101.07906.pdf}


\bibitem{JamesODonnell}
James O'Donnell, \i{et. al.},
\cq{SimModel: A domain data model for whole building energy simulation}.
\biburl{https://simulationresearch.lbl.gov/publications/simmodel-domain-data-model-whole}


\bibitem{AndersOlofsson}
Anders Olofsson,
\cq{Behavior-driven Tile Caching in Web GIS Applications}.
Chalmers, Thesis.
\biburl{https://mdpi-res.com/d_attachment/ijgi/ijgi-08-00373/article_deploy/ijgi-08-00373.pdf}



\bibitem{ParkYang}
Jiman Park and Byungyun Yang,
\cq{GIS-Enabled Digital Twin System for Sustainable
Evaluation of Carbon Emissions: A Case Study of
Jeonju City, South Korea}.
\biburl{https://www.mdpi.com/2071-1050/12/21/9186}


\bibitem{RadoslavRadev}
Radoslav Radev, 
\cq{Extending Object-Relational Mapping with Change Data Capture}.
\biburl{http://www.cs.ubbcluj.ro/~studia-i/contents/2015-1/04-Radev.pdf}


\bibitem{IsmoRakkolainen}
Ismo Rakkolainen, \i{et. al.},
\cq{State of the Art in Extended Reality -- Multimodal Interaction}.
\biburl{https://humanoptimizedxr.org/wp/wp-content/uploads/2021/06/HUMOR-State-of-the-Art-in-Extended-Reality-Multimodal-Interaction-1.pdf}

\bibitem{IsmoRakkolainenReview}
Ismo Rakkolainen, \i{et. al.},
\cq{Technologies for Multimodal Interaction in Extended
Reality -- A Scoping Review}.
\biburl{https://www.mdpi.com/2414-4088/5/12/81}



\bibitem{MarkRandall}
Mark Randall, \i{et. al.},
\cq{Geographic Object Based Image Analysis of
WorldView-3 Imagery for Urban Hydrologic
Modelling at the Catchment Scale}.
\biburl{https://www.mdpi.com/2073-4441/11/6/1133}



\bibitem{DanielleRichardson}
Danielle Richardson, 
\cq{Sustainable Urban Planning: Turning the Concrete Jungle into
Green Buildings}.
\biburl{}


\bibitem{JRio}
J. Rio, \i{et. al.},
\cq{Expansion of IFC model with structural sensors}.
\biburl{https://www.researchgate.net/publication/308164615_Expansion_of_IFC_model_with_structural_sensors}



\bibitem{FilippoSanfilippo}
Filippo Sanfilippo, \i{et. al.}, 
\cq{A Perspective Review on Integrating VR/AR with Haptics into
STEM Education for Multi-Sensory Learning}.
\biburl{https://www.mdpi.com/2218-6581/11/2/41}



\bibitem{PatrickSchultz}
Patrick Schultz, \i{et. al.},
\cq{Algebraic Databases}.
\biburl{https://arxiv.org/pdf/1602.03501.pdf}


\bibitem{EhsanShafiee}
Ehsan Shafiee, \i{et. al.},
\cq{Parallel Evolutionary Algorithm for Designing
Water Distribution Networks to Minimize
Background Leakage}.
\biburl{https://ascelibrary.org/doi/full/10.1061/\%28ASCE\%29WR.1943-5452.0000601}


\bibitem{JoshuaShinavier}
Joshua Shinavier, \i{et. al.},
\cq{Algebraic Property Graphs}.
\biburl{https://arxiv.org/pdf/1909.04881.pdf}


\bibitem{SrinathSrinivasa}
Srinath Srinivasa, \i{et. al.},
\cq{LogicFence: A Framework for Enforcing 
Global Integrity Constraints at Runtime}.
\biburl{https://ieeexplore.ieee.org/document/4041608}

\bibitem{TheilerSmarsly}
Michael Theiler and Kay Smarsly,
\cq{IFC Monitor -- An IFC schema extension for modeling structural health monitoring systems}.
\biburl{https://www.sciencedirect.com/science/article/pii/S1474034617306134}



\bibitem{ValterUotila}
Valter Uotila,  \i{et. al.},
\cq{MultiCategory: Multi-model Query Processing Meets Category
Theory and Functional Programming}.
\biburl{https://arxiv.org/pdf/2109.00929.pdf}


\bibitem{KrevelenPoelman}
D.W.F. van Krevelen and R. Poelman,
\cq{A Survey of Augmented Reality
Technologies, Applications and Limitations}.
\biburl{https://ijvr.eu/article/view/2767/8825}


\bibitem{JohanVanSoest}
Johan Van Soest, \i{et al.}, 
\cq{Towards a semantic PACS: Using Semantic Web technology to represent imaging data}.
\bibtitle{Studies in Health Technology and Informatics}, Volume 205 
(2014), pages 166-179, 
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5119276/}



\bibitem{VelazcoGarcia}
Jose D. Velazco-Garcia, \i{et. al.},
\cq{A Modular and Scalable Computational Framework for Interactive
Immersion into Imaging Data with a Holographic Augmented Reality
Interface}.
\biburl{https://pubmed.ncbi.nlm.nih.gov/33045556/}


\bibitem{RVerstraeten}
R. Verstraeten, \i{et. al.},
\cq{IFC-based calculation of the Flemish Energy Performance Standard}.
\biburl{https://biblio.ugent.be/publication/482379/file/6814885.pdf}






\bibitem{NatalieCWheating}
Natalie C. Wheating, \i{et. al.},
\cq{Embodied carbon: A framework for prioritizing
and reducing emissions in the building industry}.
\biburl{https://repository.usfca.edu/cgi/viewcontent.cgi?article=1574&context=capstone}



\bibitem{LinlinZhao}
Linlin Zhao, \i{et. al.},
\cq{An Integrated BIM–GIS Method for Planning of
Water Distribution System}.
\biburl{https://www.mdpi.com/504658}


\bibitem{XiaodongZhou}
Xiaodong Zhou, \i{et. al.},
\cq{A PDF Tile Model for Geographic Map Data}.
\biburl{https://www.mdpi.com/2220-9964/8/9/373}





}
\end{thebibliography}



