
\documentclass[10pt,twocolumn]{article}

\input{nhvm/nhv-setup-commands}
\input{nhvm/nhv-sdi-commands}
\input{nhvm/nhv-deco-commands}
\input{nhvm/nhv-sdi-shell-commands}

\include{inc/commands}
\include{inc/copyright}

\begin{document}

\title{From \cq{Naturalizing Phenomenology} to 
Formalizing Cognitive Linguistics (I): Cognitive Transform Grammar}
\author{Nathaniel Christen}

\newsavebox{\qboxi}
\newsavebox{\qboxii}

\begin{lrbox}{\qboxi}
\begin{frquote}
On conna\^{\inodot}t la c\'{e}l\`{e}bre 
affirmation de Claude L\'{e}vi-Strauss:
\q{les sciences humaines seront des sciences naturelles ou ne seront pas}.  Evidemment, sauf 
\`{a} en revenir \`{a} un r\'{e}ductionnisme dogmatique, une telle
affirmation n'est soutenable que si l'on peut suffisamment 
g\'{e}n\'{e}raliser le concept
classique de \q{naturalit\'{e}}, 
le g\'{e}n\'{e}raliser jusqu'\`{a} pouvoir y faire droit, 
comme \`{a} des ph\'{e}nom\'{e}nes naturels, aux 
ph\'{e}nom\'{e}nes d'organisation structurale. 
\\ \longdash{} Jean Petitot \cite[p. 1]{PetitotSyntaxe}
\end{frquote}
\end{lrbox}

\begin{lrbox}{\qboxii}
\begin{frquote}
The nature of any entity, I propose, divides into three aspects 
or facets, which we may call its form, appearance, and substrate.  
In an act of consciousness, accordingly, we must distinguish three 
fundamentally different aspects: its form or intentional structure, 
its appearance or subjective \q{feel}, and its substrate or 
origin.  In terms of this three-facet distinction, we can define 
the place of consciousness in the world.
\\ \longdash{} David Woodruff Smith, \cite[p. 11]{DavidWoodruffSmith}
\end{frquote}
\end{lrbox}

\twocolumn[\begin{@twocolumnfalse}

\maketitle{}
\begin{abstract}
In this paper I try to identify certain \q{paleostructures}
in language which transcend (or are somehow more fundamental 
than) the metatheoretical paradigm-opposition between 
faith in language being a \q{computable}, logico-mathematical 
system, or, conversely, a faculty bound up with overall 
human cognition, emotion, and embodiment such that nonsentient 
computers can never truly \q{understand} language.  I will, 
in fact, analyze some examples suggesting a context-sensitivity 
and a level of \q{epistemic} engagement which I feel argues 
for a register of linguistic nuance that is probably 
computationally intractable.  However, I also claim 
that \i{some} facets of language are more logically 
straightforward, and \i{some} sentences (or other 
linguistic artifacts) evince that logical register 
primarily or exclusively.  Juxtaposing these 
cases, I claim that language is not \i{intrinsically}
either tractable or non-tractable to computers or to 
any other system whose nature is essentially to carry 
out logicomathematical operations.  Instead, \q{tractability} in 
this sense is a parameter which is more or less evident 
in different artifacts.  A comprehensive theory 
must therefore address samples of language which 
are indeed strongly tractable {\mdash} so that the machinery 
of computational linguistics becomes explanatorily relevant 
{\mdash} \i{and also} examples which (via some interpretive 
or contextual complexity) are effectively \q{intractable}.  
Theories which make sense of the latter cases may be important 
to linguistic analysis even if they are not conducive 
to computational treatment or formulation.  In sum, 
different theories, with different levels of formalizability 
and of adherence to reductionist logico-mathematical 
paradigms, are appropriate for different acts of 
language.  An overall philosophy of language, then, 
rather than judging the merits or demerits of 
logical, mathematical, or computational formalization as a 
criteria of theoretical rigor, should instead seek 
to integrate diverse analyses, which paradigmatically 
differ on this issue, into a aggregated, multi-paradigm 
theoretical framework.
\end{abstract}

\begin{flushright}

\usebox{\qboxi}
\usebox{\qboxii}
\end{flushright}

\decoline{}
\vspace{3em}
\end{@twocolumnfalse}
]

\addcontentsline{toc}{section}{From \dq{Naturalizing Phenomenology} ...}

\input{man/intro/intro.ngml}
\input{man/section1/section1.ngml}

\end{document}

