\begin{thebibliography}{99}
\phantomsection \label{References}
\addcontentsline{toc}{section}{References}
{\fontfamily{lmtt}\selectfont\scriptsize



\bibitem{DavidAdger}
David Adger,
\cq{Constructions and Grammatical Explanation}.
\biburl{https://www.qmul.ac.uk/sllf/media/sllf-new/department-of-linguistics/26-QMOPAL-Adger.pdf} 


\bibitem{NadeemAkhtar}
Nadeem Akhtar, \i{et. al.},
\cq{Hierarchical Coloured Petri-Net Based Multi-Agent
System for Flood Monitoring, Prediction,
and Rescue (FMPR)}.
\biburl{https://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=8926354} 


\bibitem{KyounghoAn}
Kyoungho An, \i{et. al.},
\cq{Cloud Computing for Cyber Physical Systems:
Reliability and Security Challenges and Solutions}.
\biburl{http://www.dre.vanderbilt.edu/~gokhale/WWW/papers/CC4CPS13_FT.pdf} 


\bibitem{AneesAra}
Anees Ara, \i{et. al.},
\cq{A Secure Service Provisioning Framework for Cyber-Physical 
Cloud Computing Systems}.
\biburl{https://arxiv.org/abs/1611.00374} 


\bibitem{BerghoferUrban}
Stefan Berghofer and Christian Urban,
\cq{A Head-to-Head Comparison of
de Bruijn Indices and Names}.
\biburl{https://www.sciencedirect.com/science/article/pii/S1571066107002319} 


\bibitem{CemBozsahin}
Cem Boz\c{s}ahin,
\cq{Combinatory Logic and Natural Language Parsing}.
\biburl{https://users.metu.edu.tr/bozsahin/bozsahin-tjeecs.pdf} 


\bibitem{CemBozsahinC}
Cem Boz\c{s}ahin,
\cq{Combinatory Linguistics}.
\biburl{https://library.oapen.org/bitstream/handle/20.500.12657/24661/1005450.pdf?sequence=1&isAllowed=y} 


\bibitem{YiCai}
Yi Cai, \i{et. al.},
\cq{Sensor Data and Information Fusion to Construct Digital-Twins Virtual
Machine Tools for Cyber-Physical Manufacturing}.
\biburl{https://www.researchgate.net/publication/318291645_Sensor_Data_and_Information_Fusion_to_Construct_Digital-twins_Virtual_Machine_Tools_for_Cyber-physical_Manufacturing/link/596140e8aca2728c11e0b5fe/download} 


\bibitem{CardoneHindley}
Felice Cardone and J. Roger Hindley,
\cq{History of Lambda-Calculus and
Combinatory Logic}.
\biburl{http://www.users.waitrose.com/~hindley/SomePapers_PDFs/2006CarHin,HistlamRp.pdf} 




\bibitem{NathanielChristenCyberphysical}
Nathaniel Christen, 
\cq{Hypergraph Type Theory for 
Specifications-Conformant Code and 
Generalized Lambda Calculus}.
\intitle{Advances in Ubiquitous Computing: Cyber-Physical Systems, Smart Cities, and Ecological Monitoring}, Amy Neustein, ed., Elsevier, 2019. 


\bibitem{ChupinNilsson}
Guerric Chupin and Henrik Nilsson,
\cq{Functional Reactive Programming, Restated}.
\biburl{https://nottingham-repository.worktribe.com/preview/4922128/ppdp2019.pdf} 


\bibitem{LironCohen}
Liron Cohen, \i{et. al.},
\cq{The Effects of Effects on Constructivism}.
\biburl{https://www.cs.bgu.ac.il/~cliron/pubs/Effects.pdf} 


\bibitem{EvieCousse}
Evie Couss\'e, \i{et. al.},
\cq{Grammaticalization Meets Construction Grammar:
Opportunities, challenges and potential incompatibilities}.
\biburl{http://eviecousse.be/publications/cousse-ea-forthc-grammaticalizationmeetscxg.pdf} 


\bibitem{ReneDavid}
Ren\'e David, \i{et. al.},
\cq{A Direct Proof of the Confluence of Combinatory Strong Reduction}.
\biburl{https://arxiv.org/abs/0905.2545} 


\bibitem{ParastooDelgoshaei}
Parastoo Delgoshaei, \i{et. al.},
\cq{A Semantic Framework for Modeling and Simulation of Cyber-Physical Systems}.
\biburl{https://user.eng.umd.edu/~austin/reports.d/IARIA2014-PD-MA-AP-Journal-Paper.pdf} 


\bibitem{GhilezanKasterovic}
Silvia Ghilezan and Simona Ka\v{s}terovi\'c,
\cq{Semantics for Combinatory Logic With Intersection Types}.
\biburl{https://www.frontiersin.org/articles/10.3389/fcomp.2022.792570/full} 



\bibitem{StevenTPiantadosi}
Steven T. Piantadosi,
\cq{The Computational Origin of Representation}.
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC8300595/} 



\bibitem{JeanPierreDescles}
Jean-Pierre Descl\'es,
\cq{Reasoning in Natural Language in Using
Combinatory Logic and Topology
An Example with Aspect and Temporal Relations}.
\biburl{https://www.aaai.org/ocs/index.php/FLAIRS/2010/paper/viewFile/1350/1736} 



\bibitem{GianantonioHonsell}
Pietro Di Gianantonio and Furio Honsell,
\cq{An Abstract Notion of Application}.
\biburl{https://users.dimi.uniud.it/~pietro.digianantonio/papers/copy_pdf/ana.pdf} 


\bibitem{AlessandraDiPierro}
Alessandra Di Pierro, \i{et. al.},
\cq{On Reversible Combinatory Logic}.
\biburl{https://www.sciencedirect.com/science/article/pii/S1571066106000843} 


\bibitem{PeterFordDominey}
Peter Ford Dominey, \i{et. al.},
\cq{Dynamic Construction Grammar and Steps Towards
the Narrative Construction of Meaning}.
\biburl{https://users.cs.fiu.edu/~markaf/doc/w14.dominey.2017.procccgnlu.1.163_archival.pdf} 


\bibitem{BerndFinkbeiner}
Bernd Finkbeiner, \i{et. al.},
\cq{Synthesizing Functional Reactive Programs}.
\biburl{https://arxiv.org/pdf/1905.09825.pdf} 







\bibitem{JeanHGallier}
Jean H. Gallier,
\cq{Realizability, Covers, and Sheaves: Application to the Simply-Typed Lambda-Calculus}.
\biburl{https://repository.upenn.edu/cgi/viewcontent.cgi?article=1280&context=cis_reports} 



\bibitem{RobertGold}
Robert Gold,
\cq{Petri Nets in Software Engineering}.
\biburl{https://www.thi.de/fileadmin/daten/Working_Papers/thi_workingpaper_05_gold.pdf} 



\bibitem{MasahitoHasegawa}
Masahito Hasegawa,
\cq{The Internal Operads of Combinatory Algebras}.
\biburl{https://www.kurims.kyoto-u.ac.jp/~hassei/papers/2022_mfps2022_pre.pdf} 


\bibitem{MartinHilpert}
Martin Hilpert,
\cq{Construction Grammar and its Application to English}.
\biburl{http://members.unine.ch/martin.hilpert/CxG\%20sample.pdf} 




\bibitem{JRogerHindley}
J. Roger Hindley,
\cq{Axioms for Strong Reduction in Combinatory Logic}.
\biburl{https://www.cambridge.org/core/journals/journal-of-symbolic-logic/article/abs/axioms-for-strong-reduction-in-combinatory-logic/9B7CBE781BAE43FF5148ABE720D4517A} 





\bibitem{HindleySeldin}
J. Roger Hindley and Jonathan P. Seldin,
\cq{Lambda-Calculus and Combinators, an Introduction}.
Cambridge University Press, 2008.
\biburl{https://www.cin.ufpe.br/~djo/files/Lambda-Calculus%20and%20Combinators.pdf} 


\bibitem{HonsellSannella}
Furio Honsell and Donald Sannella,
\cq{Pre-logical Relations}.
\biburl{https://homepages.inf.ed.ac.uk/dts/pub/prelogrel-report.pdf} 


\bibitem{PetrJanda}
Petr Janda, \i{et. al.},
\cq{Implementation of the Digital Twin Methodology}.
\biburl{https://www.daaam.info/Downloads/Pdfs/proceedings/proceedings_2019/072.pdf} 


\bibitem{PaulHudak}
Paul Hudak, \i{et al.},
\cq{Arrows, Robots, and Functional Reactive Programming}.
\biburl{https://citeseerx.ist.psu.edu/document?repid=rep1&type=pdf&doi=e523884ac0c118b6e42261c6c1eaaa8fde7d57f7} 


\bibitem{MansHulden}
Mans Hulden, 
\cq{Parsing CFGs and PCFGs with a Chomsky-Sch\"utzenberger representation}.
\biburl{https://dingo.sbs.arizona.edu/~mhulden/hulden_ltc_2009.pdf} 



\bibitem{KjelstromPavolgiannis}
Adam Husted Kjelstr{\o}m and Andreas Pavolgiannis,
\cq{The Decidability and Complexity of Interleaved Bidirected
Dyck Reachability}.
\biburl{https://cs.au.dk/~pavlogiannis/publications/papers/popl22.pdf} 



\bibitem{RadekKoci}
Radek Ko\v{c}\'{\OldI}, \i{et al.},
\cq{Object Oriented Petri Nets -- Modelling Techniques Case Study}.
\bibtitle{Second UKSIM European Symposium on Computer Modeling and Simulation}, 
2008.
\biburl{https://ijssst.info/Vol-10/No-3/paper4.pdf}



\bibitem{KogkalidisMelkonian}
Konstantinos Kogkalidis and Orestis Melkonian,
\cq{$D^3$ as a 2-MCFL}.
\biburl{https://omelkonian.github.io/data/publications/d3.pdf} 


\bibitem{KohlerRolke}
Michael K\"ohler and Heiko R\"olke,  
\cq{Properties of Object Petri Nets}.
\bibtitle{International Conference on Application and Theory of Petri Nets},
2004, pages 278-297.
\biburl{https://link.springer.com/chapter/10.1007/978-3-540-27793-4_16}




\bibitem{YuanboLi}
Yuanbo Li, \i{et. al.},
\cq{Fast Graph Simplification
for Interleaved Dyck-Reachability}.
\biburl{https://research.cs.wisc.edu/wpis/papers/pldi20-graph-simplification.pdf} 



\bibitem{FeiLiu}
Fei Liu, \i{et al.},
\cq{Coloured Petri Nets for Multilevel, Multiscale and
Multidimensional Modelling of Biological Systems}.  
\bibtitle{Briefings in Bioinformatics}, Volume 20, Issue 3, 
(2019), pages 877-886.
\biburl{https://academic.oup.com/bib/article/20/3/877/4590142}





\bibitem{MichaelMoortgat}
Michael Moortgat,
\cq{A Note on Multidimensional Dyck Languages}.
\biburl{https://link.springer.com/chapter/10.1007/978-3-642-54789-8_16} 




\bibitem{SamueleMaschio}
Samuele Maschio,
\cq{On Posetal and Complete
Partial Applicative Structures}.
\biburl{https://arxiv.org/pdf/2211.11326.pdf} 


\bibitem{MelliesZeilberger}
Paul-Andr\'e Melli\`es and Noam Zeilberger,
\cq{Parsing as a Lifting Problem and the
Chomsky-Sch\"utzenberger Representation Theorem}.
\biburl{https://hal.archives-ouvertes.fr/hal-03702762/document} 


\bibitem{LauraAMichaelis}
Laura A Michaelis,
\cq{Construction Grammar}.
\biburl{https://spot.colorado.edu/~michaeli/documents/Michaelis_CG_ELL_offprint.pdf} 




\bibitem{MitchellMoggi}
John C. Mitchell and Eugenio Moggi,
\cq{Kripke-Style Models for Typed Lambda Calculus}.
\biburl{https://person.dibris.unige.it/moggi-eugenio/ftp/kripke.pdf} 


\bibitem{TiagoMuck}
Tiago M\"uck, \i{et. al.},
\cq{CHIPS-AHOy: A Predictable Holistic Cyber-Physical Hypervisor
for MPSoCs}.
\biburl{https://par.nsf.gov/servlets/purl/10119096} 


\bibitem{NeusteinChristen}
Amy Neustein and Nathaniel Christen, 
\bibtitle{Covid, Cancer, and Cardiac Care}. Elsevier, 2022. 


\bibitem{SergeyPOrlov}
Sergey P. Orlov, \i{et. al.},
\cq{Application of Hierarchical Colored Petri Nets for
Technological Facilities’ Maintenance Process Evaluation}. 
\biburl{https://www.mdpi.com/2076-3417/11/11/5100}


\bibitem{PerezNilsson}
Ivan Perez and Henrik Nilsson,
\cq{Bridging the GUI Gap with Reactive Values and Relations}. 
\biburl{https://ivanperez.io/papers/2015-HaskellSymposium-Perez-Nilsson-BridgingGUIGapReactiveValues.pdf}


\bibitem{PettitGomaa}
Robert G. Pettit IV and Hassan Gomaa,
\cq{Modeling State-Dependent Objects using Colored Petri Nets}.
\biburl{http://csis.pace.edu/~marchese/CS865/Papers/pettit-final.pdf} 




\bibitem{GiuliaRambelli}
Giulia Rambelli, \i{et. al.},
\cq{Distributional Semantics Meets Construction Grammar:
Towards a Unified Usage-Based Model of Grammar and Meaning}. 
\biburl{https://hal.archives-ouvertes.fr/hal-02146537/document}



\bibitem{IvanASag}
Ivan A. Sag, 
\cq{Sign-Based Construction Grammar: An Informal Synopsis}. 
\biburl{https://web.stanford.edu/group/cslipublications/cslipublications/pdf/BoasSag-sag-chapter.pdf}


\bibitem{AnilSawhney}
Anil Sawhney, 
\cq{Petri Net Based Simulation of Construction Schedules }. 
\biburl{https://dl.acm.org/doi/pdf/10.1145/268437.268747}






\bibitem{BorjaBordelSanchez}
Borja Bordel S\'anchez, \i{et. al.},
\cq{Enhancing Process Control in Industry 4.0 Scenarios using
Cyber-Physical Systems}.
\biburl{http://isyou.info/jowua/papers/jowua-v7n4-3.pdf} 


\bibitem{SchusterFlanagan}
Christopher Schuster and Cormac Flanagan,
\cq{Reactive Programming with Reactive Variables}.
\biburl{https://users.soe.ucsc.edu/~cormac/papers/16crow.pdf} 



\bibitem{VivekKumarSehga}
Vivek Kumar Sehga, \i{et. al.},
\cq{A Comparative Study of Cyber Physical Cloud, Cloud
of Sensors and Internet of Things: Their Ideology,
Similarities and Differences}.
\biburl{https://ieeexplore.ieee.org/document/6779411?arnumber=6779411} 

\bibitem{JonathanPSeldin}
Jonathan P. Seldin,
\cq{The Search for a Reduction in Combinatory Logic Equivalent to
$\lambda\beta$-reduction}.
\biburl{https://core.ac.uk/download/pdf/82407499.pdf} 



\bibitem{SebastianShaumyan}
Sebastian Shaumyan,
\cq{A Semiotic Theory of Language}.
\biburl{https://publish.iupress.indiana.edu/projects/a-semiotic-theory-of-language} 


\bibitem{MurraySinclair}
Murray Sinclair, \i{et. al.},
\cq{The Identification of Knowledge Gaps in the Technologies of Cyber-Physical Systems with Recommendations for Closing These Gaps}.
\biburl{https://incose.onlinelibrary.wiley.com/doi/10.1002/sys.21464} 


\bibitem{MarkSteedman}
Mark Steedman, \i{et. al.},
\cq{Plans, Affordances, and Combinatory Grammar}.
\biburl{https://homepages.inf.ed.ac.uk/steedman/papers/affordances/pelletier.pdf} 


\bibitem{KoheiSuzuki}
Kohei Suzuki, \i{et. al.},
\cq{CFRP: A Functional Reactive Programming Language for Small-Scale Embedded Systems}.
\biburl{https://www.worldscientific.com/doi/pdf/10.1142/9789813234079_0001} 



\bibitem{SzymonSzominski}
Szymon Szomi\'nski, \i{et. al.},
\cq{Development of a Cyber-Physical System
for Mobile Robot Control using Erlang}.
\biburl{https://annals-csis.org/Volume_1/pliks/246.pdf} 



\bibitem{SamVandenVonder}
Sam Van den Vonder, \i{et. al.},
\cq{Tackling the Awkward Squad for Reactive
Programming: The Actor-Reactor Model}.
\biburl{http://soft.vub.ac.be/~svdvonde/papers/ecoop2020-tackling-the-awkward-squad-the-actor-reactor-model.pdf} 



\bibitem{ValentiniaVialeb}
Silvio Valentinia and Matteo Vialeb,
\cq{A Binary Modal Logic for the Intersection Types of Lambda-Calculus}.
\biburl{https://www.sciencedirect.com/science/article/pii/S0890540103000890} 


\bibitem{AlexanderVodyaho}
Alexander Vodyaho, \i{et. al.},
\cq{Model Based Approach to Cyber–Physical Systems Status Monitoring}.
\biburl{https://www.mdpi.com/2073-431X/9/2/47/htm} 


\bibitem{WestParmer}
Richard West and Gabriel Parmer,
\cq{A Software Architecture for Next-Generation Cyber-Physical
Systems}.
\biburl{https://www.cs.bu.edu/~richwest/papers/west_cps.pdf} 


\bibitem{RyoYoshinaka}
Ryo Yoshinaka, \i{et. al.},
\cq{Chomsky-Sch\"utzenberger-Type Characterization
of Multiple Context-Free Languages}.
\biburl{http://isw3.naist.jp/IS/TechReport/report/2010003.pdf} 


\bibitem{YuZhang}
Yu Zhang, \i{et. al.},
\cq{High Fidelity Virtualization of 
Cyber-Physical Systems}.
\biburl{http://web.cecs.pdx.edu/~xie/pubs/IJMSSC13.pdf} 







}
\end{thebibliography}

